\framework: Morphology-based Entity and Relational Entity Extraction Framework for Arabic

### 2018-06-22 tex/merf/TALMajor/abstract.tex
format issues ficed: figure and table caption style

Rule-based techniques and tools to extract entities and relational entities from documents allow users to specify desired entities using natural language questions, finite state automata, regular expressions, structured query language statements, or proprietary scripts.
These techniques and tools require expertise in linguistics and programming.
\major{
They lack support of Arabic {\em morphological analysis} which is key to 
process Arabic text.
}
In this work, we present \framework; a morphology-based entity and relational entity extraction framework for Arabic text.
\framework provides a friendly interface where the user, with basic knowledge of linguistic features and regular expressions, defines tag types and interactively associates them with regular expressions defined over Boolean formulae.
Boolean formulae range over matches of Arabic morphological features, and synonymity features.
Users define relations with tuples of subexpression matches and can associate code actions with subexpressions.
\framework computes feature matches, regular expression matches, and constructs entities and relational entities from the user-defined relations.
We evaluated our work with several case studies and compared with existing application-specific techniques.
The results show that \framework requires shorter development time and effort compared to existing techniques and produces reasonably accurate results within a reasonable overhead in run time.

>>>>

Rule-based techniques and tools to extract entities and relational entities from documents allow users to specify desired entities using natural language questions, finite state automata, regular expressions, structured query language statements, or proprietary scripts.
These techniques and tools require expertise in linguistics and programming.
\major{
They lack support of Arabic {\em morphological analysis} which is key to 
process Arabic text.}
In this work, we present \framework; a morphology-based entity and relational entity extraction framework for Arabic text.
\framework provides a friendly interface where the user, with basic knowledge of linguistic features and regular expressions, defines tag types and interactively associates them with regular expressions defined over Boolean formulae.
Boolean formulae range over matches of Arabic morphological features, and synonymity features.
Users define relations with tuples of subexpression matches and can associate code actions with subexpressions.
\framework computes feature matches, regular expression matches, and constructs entities and relational entities from the user-defined relations.
We evaluated our work with several case studies and compared with existing application-specific techniques.
The results show that \framework requires shorter development time and effort compared to existing techniques and produces reasonably accurate results within a reasonable overhead in run time.

### 2018-06-22 tex/merf/TALMajor/macros.tex
changes to answer, colors, and some reviewers addressed
format issues ficed: figure and table caption style

%%%%%%%% packages %%%%%%%%%%
\usepackage{xspace}
\usepackage{arabtex}
\usepackage{array}
\usepackage{tikz}
\usepackage{hyperref}
\hypersetup{
    colorlinks=false,
    pdfborder={0 0 0},
}
\usepackage{booktabs}
\usepackage[ruled]{algorithm2e}
\usepackage{etex}
\usepackage{graphicx}
\usepackage{framed}
\usepackage{graphics}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{savesym}
\savesymbol{bigtimes}
\usepackage{mathabx}
\restoresymbol{TXF}{bigtimes}
\usepackage{utf8}
\usepackage{subfigure}
\usepackage{todonotes}
\usetikzlibrary{shapes,arrows}
\usepackage{color,soul}
\usepackage{verbatim}
\usepackage{array}
\usepackage{multicol}
\usepackage{fancyvrb}
\usepackage{relsize}
\usepackage{wasysym}
\usepackage{pbox}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%% Macros %%%%%%%%%%
\def\framework{\textsc{MERF}\xspace}
\newcommand{\itodo}[1]{\todo[inline,color=green]{\tiny #1}}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcommand{\TinyRL}[1]{{\RL{#1}}}
\newcommand{\cci}[1]{{\small \texttt{#1}}}
%%% RL commands
\newcommand{\utfrl}[1]{\setcode{utf8}\RL{#1}\setcode{standard}}
\newcommand{\notrutfrl}[1]{\transfalse\setcode{utf8}\RL{#1}\setcode{standard}\transtrue}
\newcommand{\notrrl}[1]{\transfalse\RL{#1}\transtrue}
\newcommand{\noarrl}[1]{\arabfalse\RL{#1}\arabtrue}
\def\showvrb#1{%
\texttt{\detokenize{#1}}%
}
%%% define cal
\makeatletter
\DeclareRobustCommand*\cal{\@fontswitch\relax\mathcal}
\makeatother
% done
%other 
% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\author{}
%\author{Amin A. Jaber \andauthor Fadi A. Zaraket}

\address{}
%\address{American University of Beirut, Beirut 1107 2020, Lebanon}

@@

\motscles{
%mot-cl\'e$_1$,
%mot-cl\'e$_2$,
%mot-cl\'e$_3$.
}

\resume{
%Le r\'esum\'e est \`a \'ecrire ici.
}

>>>>

%%%%%%%%% packages %%%%%%%%%%
\usepackage{xspace}
\usepackage{arabtex}
\usepackage{array}
\usepackage{tikz}
\usepackage{url}
%\usepackage{hyperref}
%\hypersetup{
%    colorlinks=false,
%    pdfborder={0 0 0},
%}
\usepackage{booktabs}
\usepackage[ruled]{algorithm2e}
%\usepackage{etex}
\usepackage{graphicx}
\usepackage{framed}
\usepackage{graphics}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{savesym}
\savesymbol{bigtimes}
\usepackage{mathabx}
\restoresymbol{TXF}{bigtimes}
\usepackage{utf8}
\usepackage{subfigure}
\usepackage{todonotes}
\usetikzlibrary{shapes,arrows}
\usepackage{color,soul}
\usepackage{verbatim}
\usepackage{array}
\usepackage{multicol}
\usepackage{fancyvrb}
\usepackage{relsize}
\usepackage{wasysym}
\usepackage{pbox}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%%%%%%%%%%% Macros %%%%%%%%%%
\newcommand{\major}[1]{{\color{black}#1}}
\def\framework{\textsc{MERF}\xspace}
\newcommand{\itodo}[1]{\todo[inline,color=green]{\tiny #1}}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcommand{\TinyRL}[1]{{\RL{#1}}}
\newcommand{\cci}[1]{{\small \texttt{#1}}}
%%% RL commands
\newcommand{\utfrl}[1]{\setcode{utf8}\RL{#1}\setcode{standard}}
\newcommand{\notrutfrl}[1]{\transfalse\setcode{utf8}\RL{#1}\setcode{standard}\transtrue}
\newcommand{\notrrl}[1]{\transfalse\RL{#1}\transtrue}
\newcommand{\noarrl}[1]{\arabfalse\RL{#1}\arabtrue}
\def\showvrb#1{%
\texttt{\detokenize{#1}}%
}
%%% define cal
\makeatletter
\DeclareRobustCommand*\cal{\@fontswitch\relax\mathcal}
\makeatother
% done
%other 
% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\author{Amin Jaber \andauthor Fadi Zaraket}

\address{American University of Beirut, Beirut 1107 2020, Lebanon}

@@

\motscles{
Arabe,
extraction d'information,
traitement du langage naturel,
entité,
entité relationnelle,
visualisation d'information,
marquage.
}

\resume{
Les techniques et outils basés sur des règles pour extraire des entités et des entités relationnelles des documents permettent aux utilisateurs de spécifier les entités souhaitées en utilisant des questions de langage naturel, des automates à états finis, des expressions régulières, des instructions de langage de requête structurées ou des scripts propriétaires.
Ces techniques et outils nécessitent une expertise en linguistique et en programmation.
Ils manquent de soutien de l'analyse morphologique arabe qui est la clé de
traiter le texte arabe.
Dans ce travail, nous présentons \framework; une entité morphologique et un cadre d'extraction d'entité relationnelle pour le texte arabe.
\framework fournit une interface conviviale où l'utilisateur, avec une connaissance de base des caractéristiques linguistiques et des expressions régulières, définit les types de balises et les associe de manière interactive aux expressions régulières définies sur des formules booléennes.
Les formules booléennes couvrent des correspondances d'entités morphologiques arabes et des caractéristiques de synonymie.
Les utilisateurs définissent des relations avec des tuples de correspondance de sous-expression et peuvent associer des actions de code à des sous-expressions.
\framework calcule des correspondances de fonctions, des correspondances d'expressions régulières et construit des entités et des entités relationnelles à partir des relations définies par l'utilisateur.
Nous avons évalué notre travail avec plusieurs études de cas et les avons comparées avec des techniques spécifiques à une application existante.
Les résultats montrent que \framework nécessite un temps et un effort de développement plus courts par rapport aux techniques existantes et produit des résultats raisonnablement précis dans une surcharge raisonnable en temps d'exécution.
}

### 2018-06-22 tex/merf/TALMajor/methodology.tex
format issues ficed: figure and table caption style

The user may inspect and refine the defined formulae, rules and relations and 
the corresponding formulae tags, rule tags, entities and relational entities
either using the GUI or directly through readable output files. 
The files are in the javascript object notation (JSON)~\cite{nolan2014javascript} 
format that is intuitive to read and modify. 
\framework separates the user defined formulae, rules, actions and relations in
a \framework tag type file and the 
matching tags in a tags files. 
The separation serves the user to apply the tag types to multiple case studies 
and to obtain a separate file of resulting tags for each.

>>>>

The user may refine the defined formulae, rules and relations and 
the corresponding formulae tags, rule tags, entities and relational entities
either using the GUI or directly through readable output files.
The files are in the javascript object notation (JSON)~\cite{nolan2014javascript} 
format that is intuitive to read and modify.
\framework separates the user defined formulae, rules, actions and relations in
a \framework tag type file and the 
matching tags in a tags files.
The separation serves the user to apply the tag types to multiple case studies 
and to obtain a separate file of resulting tags for each.

### 2018-06-22 tex/merf/TALMajor/relatedwork.tex
format issues ficed: figure and table caption style

{\bf Information Extraction.~}
The common pattern specification language (CPSL) targets system independent IE specifications~\cite{appelt1998common}. 
%CPSL consists of 
%(1) a declaration part specifying names and labels, 
%(2) a rule definition part specifying patterns, regular expressions and associated actions, and 
%(3) macro text substitution part~\cite{appelt1998common}.
\framework extends CPSL with Arabic morphological features, code actions, and user defined relations.
SystemT~\cite{chiticariu2010systemt} aims to overcome the 
%performance and expressivity 
limitations of CPSL. 
It is based on an algebraic approach to declarative information extraction, 
uses the declarative annotation query language (AQL), 
and uses an optimizer to generate high performance execution plans for the AQL rules.
%The AQL query is translated into an algebraic expression and an optimizer selects an execution plan. 
%\framework overcomes the limitations described by SystemT. 
\framework supports multiple tags per word, and supports the MRE conjunction operator which overcomes the overlapping annotation problem discussed in SystemT.
%es the overfor each word and this overcomes the lossy sequencing caused 
%by random annotation dropping. 
%\framework introduces the conjunction operation in the MRE to overcome the expressivity limitations of expressing rules with overlapping annotations.

@@

\begin{table}[tb!]
\caption{Comparison of \framework with SystemT, 
TEXTMARKER, 
Urbain, 
QARAB}
\resizebox{\columnwidth}{!}{
\begin{tabular}{l|c|c|c|c|c}
%{p{2.7cm}|p{.7cm}|p{1.2cm}|p{1.2cm}|p{1.2cm}|p{1.2cm}}
Features & \framework & SystemT & TEXT\linebreak MARKER & Urbain & QARAB\\ \hline
Query type & MRE & AQL & matching \linebreak rules & natural language & natural language \\ \hline
Morphology support& $\checked$ & - & - & OpenNLP & Parser \\ \hline
Relations & $\checked$ & - & - & $\checked$ & - \\ \hline
Actions & $\checked$ & - & - & - & - \\ \hline
Editor & $\checked$ & - & $\checked$ & - & - \\ \hline
Tag visualization & $\checked$ & - & $\checked$ & - & - \\ \hline
Graph visualization & $\checked$ & - & - & - & - \\
\end{tabular}
}
\label{tab:iecomp}
\end{table}

@@

{\bf Annotation tools.~}
MMAX2 is a manual multi-level linguistic annotation tool with an XML 
based data model~\cite{mmax2}.
%It enables the user to create, browse, visualize, and query annotations and may be able to resolve coreference tags. 
BRAT~\cite{brat} and WordFreak~\cite{wordfreak} are manual 
multi-lingual user friendly web-based annotators that allow the construction 
of entity and relation annotation corpora.
%They can be extended through plug-ins to enable automatic annotators and customized annotation visualization specifications.
Knowtator~\cite{ogren2006knowtator} is a general purpose incremental text annotation tool 
implemented as a Prot\'eg\'e~\cite{gennari2003evolution} plug-in. 
Prot\'eg\'e is an open-source platform with a suite of tools to construct domain models and knowledge-based applications with ontology. 
However, it doesn't support the Arabic language.

>>>>

{\bf Information Extraction.}
The common pattern specification language (CPSL) targets system independent IE specifications~\cite{appelt1998common}. 
%CPSL consists of 
%(1) a declaration part specifying names and labels, 
%(2) a rule definition part specifying patterns, regular expressions and associated actions, and 
%(3) macro text substitution part~\cite{appelt1998common}.
\framework extends CPSL with Arabic morphological features, code actions, and user defined relations.
SystemT~\cite{chiticariu2010systemt} aims to overcome the 
%performance and expressivity 
limitations of CPSL. 
It is based on an algebraic approach to declarative information extraction, 
uses the declarative annotation query language (AQL), 
and uses an optimizer to generate high performance execution plans for the AQL rules.
%The AQL query is translated into an algebraic expression and an optimizer selects an execution plan. 
%\framework overcomes the limitations described by SystemT. 
\framework supports multiple tags per word, and supports the MRE conjunction operator which overcomes the overlapping annotation problem discussed in SystemT.
%es the overfor each word and this overcomes the lossy sequencing caused 
%by random annotation dropping. 
%\framework introduces the conjunction operation in the MRE to overcome the expressivity limitations of expressing rules with overlapping annotations.

@@

\begin{table}[tb]
\resizebox{\columnwidth}{!}{
\begin{tabular}{l|c|c|c|c|c}
%{p{2.7cm}|p{.7cm}|p{1.2cm}|p{1.2cm}|p{1.2cm}|p{1.2cm}}
Features & \framework & SystemT & TEXT\linebreak MARKER & Urbain & QARAB\\ \hline
Query type & MRE & AQL & matching \linebreak rules & natural language & natural language \\ \hline
Morphology support& $\checked$ & - & - & OpenNLP & Parser \\ \hline
Relations & $\checked$ & - & - & $\checked$ & - \\ \hline
Actions & $\checked$ & - & - & - & - \\ \hline
Editor & $\checked$ & - & $\checked$ & - & - \\ \hline
Tag visualization & $\checked$ & - & $\checked$ & - & - \\ \hline
Graph visualization & $\checked$ & - & - & - & - \\
\end{tabular}
}
\caption{\label{tab:iecomp}Comparison of \framework with SystemT, 
TEXTMARKER, 
Urbain, 
QARAB}
\end{table}

@@

{\bf Annotation tools.}
MMAX2 is a manual multi-level linguistic annotation tool with an XML 
based data model~\cite{mmax2}.
%It enables the user to create, browse, visualize, and query annotations and may be able to resolve coreference tags. 
BRAT~\cite{brat} and WordFreak~\cite{wordfreak} are manual 
multi-lingual user friendly web-based annotators that allow the construction 
of entity and relation annotation corpora.
%They can be extended through plug-ins to enable automatic annotators and customized annotation visualization specifications.
Knowtator~\cite{ogren2006knowtator} is a general purpose incremental text annotation tool 
implemented as a Prot\'eg\'e~\cite{gennari2003evolution} plug-in. 
Prot\'eg\'e is an open-source platform with a suite of tools to construct domain models and knowledge-based applications with ontology. 
However, it doesn't support the Arabic language.

### 2018-06-22 tex/merf/TALMajor/tool.tex
format issues ficed: figure and table caption style

@@

\begin{figure}[tb!]
\setcode{utf8}
\begin{center}
  \resizebox{0.7\columnwidth}{!}{ 
  	{\relsize{-2} \input{figures/syn2ex.tex}} }
\setcode{standard}
\vspace{-2.5em}
\caption{$Syn^2($\RL{mA'}$)$}
\vspace{-3em}
\label{fig:introsynEx}
\end{center}
\end{figure}

\subsection{MRE: Morphology-based regular expressions}
\label{subsec:grammar}

\major{
Let ${\cal O} = \{ \mathit{isA}, \mathit{contains}\}$ be the set of atomic term 
predicates, where $\mathit{isA}$ and $\mathit{contains}$ denote exact match and containment, respectively.
Also, let ${\cal F} = \{ \pp, \ss, \xx, \PP, \GG, \AC\}$ be the 
set of morphological features where each morphological feature $A\in {\cal F}$ is in 
turn a set of morphological feature values.}
Given a word $w$,
a user defined constant feature value $CF\in A$,
and an integer $k, 1\le k\le 7$, 
the following are morphology-based atomic terms (MAT), {\em terms} for short.
\begin{itemize}
  \item $a(w):= \exists m \in M(w).~m=\langle p,s,x,P,G,C\rangle. r \circ CF$
where $\circ \in {\cal O}$, $r \in \{p,s,x,P,G,C\}$, and $r\in A$.
Informally, a solution vector of $w$ exists with
a feature containing or exactly matching \major{the user-chosen feature value} $CF$.
\item $a(w) := w \in Syn^k(CF), CF \in \ss$.
  Informally, this checks if $w$ is an extended synonym of a stem $CF$. 
\major{
  We limit $k$ to a maximum of $7$ since we practically noticed that 
  (1) values above $7$ introduce significant semantic noise and
  (2) the computation is expensive without a bound. 
}
\end{itemize}

@@

\major{
Consider the task we discussed in the introduction (Figure~\ref{fig:intromotiv}) 
and recall that we are interested in identifying names of people, names of places, relative positions, and numerical terms.
The table in Figure~\ref{fig:taskMBF} presents the defined formulae.
The user denotes the ``name of person'' entities with formula $N$ 
which requires the {\em category} feature in the morphological solution of a word to be {\tt Name\_of\_Person}.
The entities $n_1$, $n_2$, and $n_3$ are matches of the formula $N$ in the text.
Similarly, the user specifies formula $P$ to denote ``name of place'' entities. 
The user specifies formula $R$ to denote ``relative position'' entities, 
and defines it as a disjunction of terms that check for 
solutions matching stems such as \RL{qrb} (near) and \RL{fy} (in).
%requires the stem feature of a word to belong to a selected list of stems containing \RL{fy} and \RL{qrb}. a
Similarly, $U$ denotes numerical terms and is a disjunction of constraints 
requiring the stem feature to belong to a set of stems such as
\RL{'wl}(first), \RL{_tAny}(second), \dots \RL{`A^sr}(tenth).
}

@@

\major{
Back to the example in Figure~\ref{fig:intromotiv}.
We use the formulae defined in Figure~\ref{fig:taskMBF} to construct an MRE such as
$(P|N)\!+O?~R~O^\wedge\!2~(P|N|U)+$ where 
$|,+,?,$ and $^\wedge k$ denote disjunction, one or more, zero or one, and
up to $k$ matches, respectively.
The expression specifies a sequence of places or names of persons, 
optionally followed by a null word, 
followed by one relative position, followed by up to two possible null words, 
followed by one or more match of name of place, name of person, or numerical term.
$O?$ and $O^\wedge 2$ are used in the expression to allow for flexible matches.
%Note that the user reaches the satisfying matches by experimenting with the visualizer and the expression editor which do not require knowledge and expertise in regular expressions. 
}

@@

\subsection{User-defined relations and actions}
\label{sec:relations-actions}

@@

\subsection{\framework simulators}

@@

@@

\setcode{utf8}
\setarab
\transfalse

\begin{figure}[tb!]
\centering
\resizebox{0.7\columnwidth}{!}{
	\relsize{-1} \input{figures/reNFA.tex}
}
  \caption{Equivalent NFA of direction expression}
  \label{fig:nfaEx}
\end{figure}
\transtrue
\setcode{standard}

>>>>

\begin{figure}[tb]
\setcode{utf8}
\begin{center}
  \resizebox{0.75\columnwidth}{!}{ 
  	{\relsize{-2} \input{figures/syn2ex.tex}} }
\setcode{standard}
\vspace{-3em}
\caption{$Syn^2($\RL{mA'}$)$}
\vspace{-2em}
\label{fig:introsynEx}
\end{center}
\end{figure}

@@

\vspace{-1em}
\subsection{MRE: Morphology-based regular expressions}
\label{subsec:grammar}

\major{
Let ${\cal O} = \{ \mathit{isA}, \mathit{contains}\}$ be the set of atomic term 
predicates, where $\mathit{isA}$ and $\mathit{contains}$ denote exact match and containment, respectively.
Also, let ${\cal F} = \{ \pp, \ss, \xx, \PP, \GG, \AC\}$ be the 
set of morphological features where each morphological feature $A\in {\cal F}$ is in 
turn a set of morphological feature values.}
Given a word $w$,
a user defined constant feature value $CF\in A$,
and an integer $k, 1\le k\le 7$, 
the following are morphology-based atomic terms (MAT), {\em terms} for short.
\begin{itemize}
  \item $a(w):= \exists m \in M(w).~m=\langle p,s,x,P,G,C\rangle. r \circ CF$
where $\circ \in {\cal O}$, $r \in \{p,s,x,P,G,C\}$, and $r\in A$.
Informally, a solution vector of $w$ exists with
a feature containing or exactly matching \major{the user-chosen feature value} $CF$.
\item $a(w) := w \in Syn^k(CF), CF \in \ss$.
  Informally, this checks if $w$ is an extended synonym of a stem $CF$. 
\major{We limit $k$ to a maximum of $7$ since we practically noticed that 
  (1) values above $7$ introduce significant semantic noise and
  (2) the computation is expensive without a bound.}
\end{itemize}

@@

\major{
Consider the task we discussed in the introduction (Figure~\ref{fig:intromotiv}) 
and recall that we are interested in identifying names of people, names of places, relative positions, and numerical terms.
Table~\ref{tab:taskMBF} presents the defined formulae.
The user denotes the ``name of person'' entities with formula $N$ 
which requires the {\em category} feature in the morphological solution of a word to be {\tt Name\_of\_Person}.
The entities $n_1$, $n_2$, and $n_3$ are matches of the formula $N$ in the text.
Similarly, the user specifies formula $P$ to denote ``name of place'' entities. 
The user specifies formula $R$ to denote ``relative position'' entities, 
and defines it as a disjunction of terms that check for 
solutions matching stems such as \RL{qrb} (near) and \RL{fy} (in).
%requires the stem feature of a word to belong to a selected list of stems containing \RL{fy} and \RL{qrb}. a
Similarly, $U$ denotes numerical terms and is a disjunction of constraints 
requiring the stem feature to belong to a set of stems such as
\RL{'wl}(first), \RL{_tAny}(second), \dots \RL{`A^sr}(tenth).
}

@@

\major{
Back to the example in Figure~\ref{fig:intromotiv}.
We use the formulae defined in Table~\ref{tab:taskMBF} to construct an MRE such as
$(P|N)\!+O?~R~O^\wedge\!2~(P|N|U)+$ where 
$|,+,?,$ and $^\wedge k$ denote disjunction, one or more, zero or one, and
up to $k$ matches, respectively.
The expression specifies a sequence of places or names of persons, 
optionally followed by a null word, 
followed by one relative position, followed by up to two possible null words, 
followed by one or more match of name of place, name of person, or numerical term.
$O?$ and $O^\wedge 2$ are used in the expression to allow for flexible matches.
%Note that the user reaches the satisfying matches by experimenting with the visualizer and the expression editor which do not require knowledge and expertise in regular expressions. 
}

@@

\vspace{-2em}
\subsection{User-defined relations and actions}
\label{sec:relations-actions}

@@

\vspace{-1em}
\subsection{\framework simulators}

@@

\setcode{utf8}
\setarab
\transfalse
\begin{figure}[tb]
\centering
\resizebox{0.75\columnwidth}{!}{
	\relsize{-1} \input{figures/reNFA.tex}
}
\vspace{-1em}
  \caption{\label{fig:nfaEx}Equivalent NFA of direction expression.}
  \vspace{-1em}
\end{figure}
\transtrue
\setcode{standard}

@@
